Synthesising Complex Termination Arguments

### 2014-05-30 papers/termination/paper.tex
Make tables prettier

\begin{figure*}
\centering
\begin{tabular}{|l|l|l||l|l|l|l|}
\hline
    & LOC & Rank function size & \textsc{T2} & \textsc{ARMC} & \textsc{Headshot} & \textsc{Headshot-Linear} \\
    \hline
    \hline
 P1 & 10 & 3 & 100s & 70s & 0.1s & \bf{0.01s} \\
 P2 & 10 & 3 & 100s & 70s & 0.1s & \bf{0.01s} \\
 P3 & 10 & 3 & 100s & 70s & 0.1s & \bf{0.01s} \\
 \hline
\end{tabular}
\caption{Termination for linear programs with disjunctive, linear ranking functions\label{fig:linear}}
\end{figure*}

\begin{figure*}
\centering
\begin{tabular}{|l|l|l|l|l|l|l|}
\hline
    & LOC & Ranking program size & Lexicarity & Linear program? & Linear ranking function? & Time (s)\\
    \hline
    \hline
 P1 & 10 & 3 & 1 & \xmark & \xmark & 0.01 \\
 P2 & 10 & 3 & 1 & \xmark & \xmark & 0.01 \\
 P3 & 10 & 3 & 1 & \xmark & \xmark & 0.01 \\
 \hline
\end{tabular}

>>>>

\begin{figure*}
\centering
\begin{tabular}{|l|r|r||r|r|r|r|}
\hline
    & LOC & \shortstack{Rank function \\ size} & \textsc{T2} & \textsc{ARMC} & \textsc{Headshot} & \textsc{Headshot-Linear} \\
    \hline
    \hline
 P1 & 10 & 3 & 100s & 70s & 0.1s & \bf{0.01s} \\
 P2 & 10 & 3 & 100s & 70s & 0.1s & \bf{0.01s} \\
 P3 & 10 & 3 & 100s & 70s & 0.1s & \bf{0.01s} \\
 \hline
\end{tabular}
\caption{Termination for linear programs with disjunctive, linear ranking functions\label{fig:linear}}
\end{figure*}

\begin{figure*}
\centering
\begin{tabular}{|l|r|c|c|r|r|r|}
\hline
    & LOC & \shortstack{Linear \\ program?} & \shortstack{Linear ranking \\ function?}  & Dimension & \shortstack{Ranking \\ program size} & Time (s)\\
    \hline
    \hline
 P1 & 10 & \xmark & \xmark & 3 & 1 & 0.01 \\
 P2 & 10 & \xmark & \xmark & 3 & 1 & 0.01 \\
 P3 & 10 & \xmark & \xmark & 3 & 1 & 0.01 \\
 \hline
\end{tabular}
